\documentclass[12pt,a4paper]{report} 
\usepackage{vntex}
\usepackage{graphicx}
 \usepackage{wrapfig}
\usepackage{longtable}
\usepackage{tocbibind} 
\usepackage{amsmath}
\usepackage{amssymb}
\allowdisplaybreaks
\usepackage[unicode]{hyperref}
\DeclareUnicodeCharacter{00A0}{ }
%================================= header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\sectionmark}[1]{\markboth{}{\thesection~#1}}
\renewcommand{\subsectionmark}[1]{}
\fancyhf{} % xoá các định dạng hiện tại đối với phần tựa đề trang
\fancyfoot[RO,RE]{\bfseries\thepage}
\fancyhead[LO,LE]{\bfseries\rightmark}
\fancyfoot[LO,LE]{\small{Trường đại học Bách Khoa \\ Khoa khoa học và kỹ thuật
máy tính}}
%\fancyhead[RE]{\bfseries\leftmark}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.2pt}
\addtolength{\headheight}{1cm} % tạo khoảng trống cho vạch ngang
\fancypagestyle{plain}{%
\fancyhead{} % chỉnh phần tựa đề cho trang trắng
\renewcommand{\headrulewidth}{0pt} % và đường kẻ ngang
}
%================================ add subsubsection 
\usepackage{titlesec}

\setcounter{secnumdepth}{4} 

\titleformat{\subsubsection}
{\normalfont\normalsize\bfseries}{\thesubsubsection}{1em}{}
\titlespacing*{\subsubsection}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

%================================ set title format
\usepackage{titlesec}
\newcommand\tab[1][1cm]{\hspace*{#1}} 

\addtolength{\voffset}{-1.5cm}
\addtolength{\textheight}{1.5cm}

%==============================
%\setlength{\parindent}{2pt}
\begin{document}
\pagenumbering{roman}
\input{title_page_1} 

\include{LoiNoiDau}

%===============================
%=========== gioi thieu =============
%==============================
\tableofcontents
\pagebreak
\listoffigures
\pagebreak 
\listoftables  
\pagebreak

\chapter*{Danh mục chữ viết tắt}
\thispagestyle{plain} 
\addcontentsline{toc}{chapter}{Danh mục chữ viết tắt}
\begin{tabbing}
\hspace{3cm}\= \kill
PCA\>Principal Component Analysis\\
SVD\>Singular Value Decomposition\\
EM\>Expectation Maximization\\
SOM\>Self Organizing Maps\\
SVM\>Support Vector Machine\\
BMU\>Best Matching Unit\\
IDS\>Intrusion Detection Systems\\
IPS\>Intrusion Prevention Systems\\
NIDS\>Network-based Intrusion Detection Systems\\
HIDS\>Host-based Intrusion Detection Systems\\
OSSEC\>Open Source HIDS SECurity\\
ADFA\>Australian Defence Force Academy\\
ACL\>Access Control List\\
BSD\>Berkeley Software Distribution\\
HTTP\>Hyper-Text Transfer Protocol
\end{tabbing}

\pagebreak 

\pagenumbering{arabic}
%======================Introduction=============
\include{C1_GioiThieu}
\include{C2_CTLienQuan} 
%====================== Ly thuyet ==================
\include{C3_NenTangLT}
\include{C4_GTGomCum}
\include{C5_OSSEC}
\include{C6_ThietKe}
\include{C7_KLHuongPhatTrien}

 
\pagebreak
\begin{thebibliography}{9}  

\bibitem{JohnSOM}
John A. Bullinaria, \emph{Self Organizing Maps: Fundamentals- Introduction to
Neural Networks: Lecture 16}. 2004

\bibitem{KohonenSOM}
Shyam M. Guthikonda, \emph{Kohonen Self-Organizing Maps}. Wittenberg
University. 2005

\bibitem{MehotraMohanRankaSOM}
Mehotra, K., Mohan, C. K., Ranka. S, \emph{Self-Organizing Maps (SOMs)}.
Elements of Artificial Neural Networks. MIT Press. 1997.

\bibitem{SVD} 
Kirk Baker, \emph{Singular Value Deomposition Tutorial}. 2005.

\bibitem{Modeling Syscall}
Eleazar Eskin, Wenke Lee, Salvatore J. Stolfo, \emph{Modeling System Calls
for Intrusion Detection with Dynamic Window Sizes}. DARPA Information
Survivability Conference \& Exposition II, 2001. DISCEX '01. Proceedings. 2001.

\bibitem{Bottou95convergenceproperties}
 Léon Bottou, Yoshua Bengio. \emph{Convergence Properties of the K-Means
 Algorithms}. MIT Press. 1995.
 
 \bibitem{XplaformHIDS}
Gideon Creech. \emph{Developing a high-accuracy cross platform Host-Based
Intrusion Detection System capable of reliably detecting zero-day attacks}. 
2014.

\bibitem{MachineLearningLec}
Andrew Ng. \emph{Lecture Notes – CS229 Machine Learning}. 2012

\bibitem{ossec}
Andrew Hay, Daniel Cid, Rory Bay, \emph{OSSEC Host-Based Intrusion Detection
Guide}. Syngress. 2008

\end{thebibliography}
\end{document}
